r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-26 r-package/paper2020/paper2020.Rmd
changes paper output formats

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: "Routing is a key step in transport planning. Nonetheless, researchers and practitioners still face challenges regarding this task, such as the cost of licensed software and the long computation times to run complex scenarios. Conveyal's R<sup>5</sup> is a multimodal transport network router that offers meaningful planning features, such as accounting for service reliability issues and returning multiple travel time estimates and itineraries for a single origin/destination pair. This paper describes r5r, an open source R package built on top of R<sup>5</sup> that allow users to efficiently compute travel time matrices and generate detailed itineraries between a set of origins and destinations at no expense. The development of this package contributes to the transport field as it offers an easy-to-use powerful tool for robust planning and research."
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

```{r, message = FALSE}
order_data <- ttm[, .(fromId, toId, travel_time_p025, travel_time_p050, travel_time_p075)]
order_data <- order_data[order(travel_time_p050, travel_time_p025, travel_time_p075)]
id_order   <- order_data[, id := paste0(fromId, "_", toId)]$id

@@

ggplot(plot_data) + 
   geom_point(aes(id, travel_time, color = percentil), alpha = 0.1, size = 1) + 
   theme_minimal() +
   theme(axis.title.x = element_blank(), axis.text.x = element_blank())
```

Notice that the leftmost origin/destination pairs do not exhibit any variation in the distribution of their travel time along the time window. This is because the trips between such pairs rely solely on walking to be completed, therefore are not susceptible to transit reliability issues.

>>>>

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
abstract: "Routing is a key step in transport planning. Nonetheless, researchers and practitioners still face challenges regarding this task, such as the cost of licensed software and the long computation times to run complex scenarios. Conveyal's R<sup>5</sup> is a multimodal transport network router that offers meaningful planning features, such as accounting for service reliability issues and returning multiple travel time estimates and itineraries for a single origin/destination pair. This paper describes r5r, an open source R package built on top of R<sup>5</sup> that allow users to efficiently compute travel time matrices and generate detailed itineraries between a set of origins and destinations at no expense. The development of this package contributes to the transport field as it offers an easy-to-use powerful tool for robust planning and research."
urlcolor: blue
bibliography: references.json
---

@@

```{r, message = FALSE}
percentiles <- 1:100

ttm <- travel_time_matrix(r5r_core,
                          origins = points,
                          destinations = points,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          max_walk_dist = max_walk_dist,
                          max_trip_duration = max_trip_duration,
                          time_window = time_window,
                          percentiles = percentiles)

order_data <- ttm[, .(fromId, toId, travel_time_p025, travel_time_p050, travel_time_p075)]
order_data <- order_data[order(travel_time_p050, travel_time_p025, travel_time_p075)]
id_order   <- order_data[, id := paste0(fromId, "_", toId)]$id

@@

ggplot(plot_data) + 
   geom_point(aes(id, travel_time), alpha = 0.02, size = 1) + 
   theme_minimal() +
   theme(axis.title.x = element_blank(), axis.text.x = element_blank())
```

Note that the leftmost origin/destination pairs do not exhibit any variation in the distribution of their travel time along the time window. This is because the trips between such pairs rely solely on walking to be completed, therefore are not susceptible to transit reliability issues.
